Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-06-04 Master Thesis/synopsis.tex
Add bibliography entry for O. Endler's valuation theory

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension (\cite{ZS60}, Ch. VI, §11, Lemma 2).
\end{proof}

>>>>

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers (\cite{En72}, Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rrank}(w) = \operatorname{rrank}(v)$ in an algebraic field extension (\cite{ZS60}, Ch. VI, §11, Lemma 1).
\end{proof}
